Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-18 analysis/paper/paper.Rmd
Updated methods to include more information regarding univariate k-means, as well as a citation

  Reduction categories were based upon dorsal cortex percentages were discretized based upon standard cut points. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995). Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average.

Papageorgiou (2020)

@@

>>>>

  Reduction categories were based upon dorsal cortex percentages were discretized based upon standard cut points. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995). Mass clusters were generated using univariate k-means, with the end result being 6 mass clusters, with mass cluster 1 having the least mass on average and 6 having the greatest mass on average. Univariate k-means is a non-hierarchical clustering technique that creates a set number of groups equal to k, with points being assigned to groups in such a manner that the total distances between each point and mean of the group in minimized. For more information on univariate k-means, Papageorgiou (2020) examines the various different statistical techniques (including k-means) that can be applied in an archaeological setting, specifically in the study of ceramics.

@@

<!-- QH: added more info on univariate k-means, as well as a citation  -->
